Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-07-24 review/response.Rmd

The authors need to convince readers (users) this kind of environment is good for daily EDA for the real world of big data/data science.

**We have revised the introduction to improve the motivation to make this clear.**

Example(s) with very large number (at least hundreds) of dimensions should be included in the study.

**The simulation study and the applications reveal that the current methods are efficient only in smaller parameter spaces. There are two components that would be required to scale it to examples with hundreds of dimensions: (1) fast computational engine, (2) an efficient optimiser. Both of these would require major implementation work. We have explained this now in the discussion section.** XXX check

**However, as we now explain in the introduction, we have previously considered an example where the dimensionality was around 60, and it worked best to reduce the dimensionality using PCA as a pre-processing step, because this explained most of the variability (Cook, Laa, and Valencia 2018).**

@@

2) According to the aims & scope of the journal, Computational Statistics, this article should keep the content and discussion relevant more focused on the computational aspects.

**We are really not sure what is being requested here. We have tried to focus the content in the paper on the compututational aspects of the work, and have kept it concise and to the point. The paper is at a reasonable length. The appendix has some details that broaden the discussion. If there are more parts that the reviewer suggests should be shifted to an appendix, we would be happy to do that.**

3) Although the target of this article focuses on the dataset with two-dimensional structure (d=2), it is worth to discuss the possibility (or give some suggestions) of applying the proposed procedure to the situation where d > 2.

**We thank the referee for the suggestion. Many of the available index functions also work for d>2, for example the ones in the tourr package work for arbitrary dimension. The work in this paper focuses on studying a selection of indexes designed for 2D. However, the same diagnostics could be applied generally to any dimension projection index. We have commented on this in the discussion.** XXX CHECK THIS.

### 2019-07-24 scagnostics.Rmd
Working on revision.

The work also reveals inadequacies in the tour optimization algorithm, that may benefit from newly developed techniques and software tools. Exploring this area would help improve the guided tours.

\textcolor{red}{To use the existing index functions on real-world datasets we recommend to either use the tourr package directly, or if interaction is required to call the guided tour via the graphical interface available in the galahr [XXX Ref] package. Both packages contain examples to show how the guided tour can be used with different index functions.}

#The tour is also lacking a portable, easy to use interface that would enable user interactions like stopping, re-starting, saving optimal projections, and development of a graphical user interface, similar to the tourrGui [@tourrGui] (now archived), would help users and projection pursuit researchers.

>>>>

The work also reveals inadequacies in the tour optimization algorithm, that may benefit from newly developed techniques and software tools. Exploring this area would help improve the guided tours.
\textcolor{red}{In particular these developments would enable the application of guided tours to datasets with large number of dimensions.}

\textcolor{red}{To use the existing index functions on real-world datasets we recommend to either use the tourr package directly, or if interaction is required to call the guided tour via the graphical interface available in the galahr [XXX Ref] package, superseding the now archived tourrGui [@tourrGui]. Both packages contain examples to show how the guided tour can be used with different index functions.}
